API design for machine learning software: experiences from the scikit-learn project

### 2013-08-05 paper.tex
Comma not needed

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named constant hyper-parameter values
(e.g., the $C$ constant in SVMs)
and can be considered as a function
that maps these values to actual learning algorithms.
The constructor of an estimator does not see any actual data, nor does it perform any actual learning.
All it does is attach the given parameters to the object.
For the sake of convenient model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
For ease of use, default hyper-parameter values are also provided
for all built-in estimators.
These default values are set to be relevant in most common
situations in order to make estimators as effective as possible
\textit{out-of-box} for non-experts.

Actual learning is performed by the \texttt{fit} method. This method is called
with training data (e.g., supplied as two arrays \texttt{X\_train} and
\texttt{y\_train} in supervised learning estimators). Its task is to run a
learning algorithm and to determine model-specific parameters from the training
data and set these as attributes on the estimator object. As a convention, the
parameters learned by an estimator are exposed as public attributes with names
suffixed with a trailing underscore (e.g., \texttt{coef\_} for the
learned coefficients of a linear model),
again to facilitate model inspection.
In the partial application view,
\texttt{fit} is a function from data to a model of that data.
As such, it always returns the estimator object it was called on,
which now serves as a model of its input and can be used to perform predictions or transformations of input data.
The choice to let a single object serve dual purpose as estimator and model
simplifies the \sklearn class hierarchy
compared to an approach where estimators and models are separated.

>>>>

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named constant hyper-parameter values
(e.g., the $C$ constant in SVMs)
and can be considered as a function
that maps these values to actual learning algorithms.
The constructor of an estimator does not see any actual data, nor does it perform any actual learning.
All it does is attach the given parameters to the object.
For the sake of convenient model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
For ease of use, default hyper-parameter values are also provided
for all built-in estimators.
These default values are set to be relevant in many common
situations in order to make estimators as effective as possible
\textit{out-of-box} for non-experts.

Actual learning is performed by the \texttt{fit} method. This method is called
with training data (e.g. supplied as two arrays \texttt{X\_train} and
\texttt{y\_train} in supervised learning estimators). Its task is to run a
learning algorithm and to determine model-specific parameters from the training
data and set these as attributes on the estimator object. As a convention, the
parameters learned by an estimator are exposed as public attributes with names
suffixed with a trailing underscore (e.g., \texttt{coef\_} for the
learned coefficients of a linear model),
again to facilitate model inspection.
In the partial application view,
\texttt{fit} is a function from data to a model of that data.
As such, it always returns the estimator object it was called on,
which now serves as a model of its input and can be used to perform predictions or transformations of input data.
The choice to let a single object serve dual purpose as estimator and model
simplifies the \sklearn class hierarchy
compared to an approach where estimators and models are separated.
